Paper without a name

### 2014-05-09 Article.tex
haha

\begin{figure}
 \centering
 \begin{minipage}{.5\textwidth}
 	\centering
	 \def\svgwidth{0.2\textwidth}
	 \includesvg{svg/2wires_box}
	 \caption{Trivial solution for 2 wires}
 \end{minipage}%
 \begin{minipage}{.5\textwidth}
 	\centering
	 \def\svgwidth{0.5\textwidth}
	 \includesvg{svg/4wires_box}
	 \caption{Simple non-optimal solution for 4 wires}
 \end{minipage}
\end{figure}

\begin{figure}
	\centering
	\def\svgwidth{0.6\textwidth}
	\includesvg{svg/8wires_box}
	\caption{Simple non-optimal solution for 8 wires}
\end{figure}

@@

To understand the problem, we first tried manually to get $opt_n$ for very small
values of $n$.\\
For $n=2$, the answer is quite simple~: One box is enough and necessary to swap
the two wires.\\
For $n=3$, two boxes aren't enough. Using a permutation, we can consider that
the first box swap the wires 1 and 2, and that the second box swap the wires 2
and 3.  Then the permutation $(1,3)$ can't be generated with this configuration.
Hence, we have $opt_3=3$.

@@

>>>>

@@

To understand the problem, we first tried manually to get $opt_n$ for very small
values of $n$.\\
For $n=2$, the answer is quite simple~: One box is enough and necessary to swap
the two wires.\\

\begin{figure}
 \centering
 \begin{minipage}{.5\textwidth}
 	\centering
	 \def\svgwidth{0.3\textwidth}
	 \includesvg{svg/boxsys-2-1}
	 \caption{Trivial solution for 2 wires}
 \end{minipage}%
 \begin{minipage}{.5\textwidth}
 	\centering
	 \def\svgwidth{0.5\textwidth}
	 \includesvg{svg/boxsys-4-6}
	 \caption{Simple non-optimal solution for 4 wires}
 \end{minipage}
\end{figure}

For $n=3$, two boxes aren't enough. Using a permutation, we can consider that
the first box swap the wires 1 and 2, and that the second box swap the wires 2
and 3.  Then the permutation $(1,3)$ can't be generated with this configuration.
Hence, we have $opt_3=3$.

\begin{figure}
	\centering
	\def\svgwidth{0.7\textwidth}
	\includesvg{svg/boxsys-8-20}
	\caption{Simple non-optimal solution for 8 wires}
\end{figure}

On these representations, a box is a horizontal line that can swap the wires the points are on.

@@

\begin{figure}
	\centering
	\begin{minipage}{.5\textwidth}
		\centering
		\def\svgwidth{0.7\textwidth}
		\includesvg{svg/boxsys-5-9}
		\caption{Solution for 5 wires}
	\end{minipage}%
	\begin{minipage}{.5\textwidth}
		\centering
		\def\svgwidth{0.85\textwidth}
		\includesvg{svg/boxsys-6-12}
		\caption{Solution for 6 wires}
	\end{minipage}
\end{figure}
